\documentclass{ExpressiveCoverLetter}

\begin{document}

\coverletterheader[
    firstname=Matthew,
    middleinitial=D,
    lastname=Tankersley,
    email=matt.d.tankersley@gmail.com,
    % phone=123-456-7890,
    linkedin=matthew-tankersley,
    github=mdtanker,
    % city=Wellington,
    % state=New Zealand
]

\vspace{0.25in}
\today
\vspace{0.15in}


Dear Dr. Heagy,

I am writing to express interest in the recently advertised postdoctoral
position "Computational geophysics for mineral exploration and mining" at the
UBC Geophysical Inversion Facility.
A little bit about me; I am from
Colorado, USA, and received my undergraduate degree in Geology from
Colorado College in 2018.
I then moved to Wellington, New Zealand, in
2019 to begin my Ph.D. in Geophysics at the Antarctic Research Centre at the Victoria
University of Wellington.
I submitted my Ph.D. thesis two weeks ago and will defend in the coming months.

During this Ph.D., I used airborne gravity and magnetic data to
investigate the Earth beneath the floating Ross Ice Shelf in Antarctica.
The first section of my Ph.D., attached in my email to
you, used airborne magnetics data and a
depth-to-source technique to identify the contact between magnetic
basement rock and overlying non-magnetic sediments. This research and
the underlying code and Jupyter Notebooks were
published open-access in \textit{Geophysical
    Research Letters} (\url{https://doi.org/10.1029/2021GL097371}).
The second section of my thesis involved developing a non-linear geometric gravity
inversion, written in Python. I used this inversion with airborne gravity data
and seismic constraints to recover a model of bathymetry, as well as spatially variable uncertainty, beneath the
Ross Ice Shelf. If you would like any more details on this inversion or
the implementation of it for the Ross Ice Shelf, I am happy to share my submitted
thesis with you.

In general, my main research interest lies in the use of large-scale geophysical
exploration to better understand the natural world. While many
geophysical techniques involve an element of non-uniqueness, I believe when
combined with appropriate geologic knowledge and constraints, and by
systematically addressing uncertainties, these techniques can provide
valuable insights into the underlying geology. I am interested in a
variety of applications of geophysical exploration, including geothermal potential, mineral
resources, and cryosphere investigation.


% My primary objectives were to better understand the components of the
% Earth which influence how the ice sheet behaves. These components
% include the geologic composition and shape of
% the seafloor beneath the ice shelf.


% The first chapter of the thesis used
% airborne magnetics data collected over the entire ice shelf and a
% depth-to-magnetic source technique, Werner deconvolution, to model the contact
% between magnetic basement rock, and overlying sediments. From this, we
% found a continuous drape of non-magnetic sediments over the seafloor, as
% well as several distinct depocenters with several kilometers of
% sediment. This research was published open-access in Geophysical Research
% Letters (\url{https://doi.org/10.1029/2021GL097371}) and the code and
% Jupyter notebooks are available in a Github repository (\url{https://github.com/mdtanker/RIS_basement_sediment}).


% The second main objective of my Ph.D. was to model the bathymetry
% beneath the Ross Ice Shelf through a gravity inversion. This style
% of non-linear geometric gravity inversion for bathymetry is commonly
% used in sub-ice shelf settings but is almost exclusively accomplished with
% proprietary, expensive, and poorly documented inversion algorithms (e.g.
% Oasis Montaj). Instead, I choose to develop a new inversion written in Python, utilizing several existing
% tools, such as \textit{Harmonica} for forward gravity calculations and
% \textit{Scipy} for least-squares regression.
% As a means of testing the inversion's capabilities, and learning about
% the sensitivity of the inversion to various data components, such as
% noise in the gravity data and the number of \textit{a priori}
% bathymetry measurements, I performed a suite of inversions on
% synthetic datasets.
% I first tested this inversion on a suite of synthetic models and finally
% used the inversion to create a new model of bathymetry beneath the Ross
% Ice Shelf, revealing some large differences with past models of
% bathymetry.
% From this work, I plan in the next few months to publish a methods paper on the inversion and a results paper on the Ross Ice Shelf.
% If you would like any more details, I am happy to share my submitted
% thesis with you.

% I am passionate about geophysical exploration and its applications to studying the Earth.
While I haven't worked extensively with EM data, I
would be very excited to incorporate a new tool into my repertoire. I
believe my knowledge of inversion theory, my experience coding in
Python, both independently and in a collaborative setting (my
contributions to Fatiando packages), and my commitment to conducting open-source
research makes me well-suited for this postdoc.
Additionally, I think my past experiences and collaborations could
bring interesting opportunities for using EM data to study the sub-ice
environment of Antarctica.


Thank you for taking the time to review my application. I look forward
to hopefully meeting with you to further discuss my
qualifications for this postdoc. If you have any questions, please feel free to
email me at \href{mailto:matt.d.tankersley@gmail.com}{matt.d.tankersley@gmail.com}.


For letters of reference, please feel free to use the below contacts:
\begin{itemize}
    \item Dr. Huw Horgan, Ph.D. Primary Supervisor: \href{mailto:huw.horgan@slf.ch}{huw.horgan@slf.ch}
    \item Dr. Fabio Caratori-Tontini, Ph.D. Secondary Supervisor: \href{mailto:fabio.caratori.tontini@unige.it}{fabio.caratori.tontini@unige.it}
    \item Dr. Christine Siddoway, Collaborator: \href{mailto:csiddoway@coloradocollege.edu}{csiddoway@coloradocollege.edu}
\end{itemize}


Sincerely,

\vspace{.15in}

Matt Tankersley

\end{document}